---
author: Students
title: Assignment 1
date: 2023-01-06
date-format: long
include-in-header: |
    \usepackage{fancyvrb}
format:
    pdf:
        toc: false
        number-sections: true
        number-depth: 2
        colorlinks: true
        geometry:
            - top = 30mm
            - bottom = 30mm
            - left = 20mm
            - right = 20mm
        documentclass: article
        papersize: dina4
---

```{r, echo=FALSE}

suppressMessages(source("main.r"))

```


# Question 1

## i)

```{r, results='asis', echo=FALSE, fig.pos='H'}

stargazer(
    model_1_i,
    header = FALSE,
    title = "OLS regression for log-earnings on schooling, age, and age squared." ,
    label = "model1i"
)

```

From Table \ref{model1i} can be observed that only the intercept and \verb+schooling+ are significant. 
Both are significant at the $1\%$-significance level.
For a given worker, an additional year of schooling is associated with a $(e^{0.216} - 1)\,\cdot\,100 \approx 24.11\%$ increase in wage.
The intercept and explanatory variables explain $81.5\%$ of the variation in \verb+logwage+.

## ii)

Low-wage workers may be incentivized to stay at home to take care of their families more than high-wage workers.
Then, instead of having a low \verb+logwage+, these workers have missing values for \verb+logwage+.
As a result, the OLS estimate of the \verb+schooling+ coefficient will be biased downwards, since the measurement of the relationship between \verb+logwage+ and \verb+schooling+ is shifted towards workers who earn higher wages (i.e., the slope is estimated to be smaller than it truly is). Since a larger sample does not alleviate this problem, the OLS estimates will also be inconsistent.

<!-- formulate sample selection model -->

## iii)

<!-- "you need to have a variable that explains why they are in the sample but not why they are getting higher wages" -> use economic theory (assumptions); cannot use t-tests on coefficients on SELECTED SAMPLE -->
<!-- maybe provide some counterarguments to exclusion restriction  -->

## iv)

## v)

# Question 2

## i)

## ii)

## iii)