---
author: Students
title: Assignment 1
date: 2023-01-06
date-format: long
include-in-header: |
    \usepackage{fancyvrb}
format:
    pdf:
        toc: false
        number-sections: true
        number-depth: 2
        colorlinks: true
        geometry:
            - top = 30mm
            - bottom = 30mm
            - left = 20mm
            - right = 20mm
        documentclass: article
        papersize: dina4
---

```{r, echo=FALSE}

suppressMessages(source("main.r"))

```


# Question 1

## i)

```{r, results='asis', echo=FALSE, fig.pos='H'}

stargazer(
    model_1_i,
    header = FALSE,
    title = "OLS regression for log-earnings on schooling, age, and age squared." ,
    label = "model1i"
)

```

From Table \ref{model1i} can be observed that only the intercept and \verb+schooling+ are significant. 
Both are significant at the $1\%$-significance level.
For a given worker, an additional year of schooling is associated with a $(e^{0.216} - 1)\,\cdot\,100 \approx 24.11$ increase in wage.
The intercept and explanatory variables explain $81.5\%$ of the variation in \verb+logwage+.

## ii)

## iii)

## iv)

## v)

# Question 2

## i)

## ii)

## iii)